---
title: "Lab 8"
author: "Anna Zauner"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(modelsummary)
library(broom)
```


```{r}
homes <- read_csv(here("data", "slo_homes.csv")) 
  
```

A little bit of cleaning:

Make a subset calles homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```


## Do a litle exploring of our data 

Summary statistics (home price, based on city and sale status)

Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status


```{r}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

## Actually I dont even wanna run this code: eval = FALSE

ggplot(data = homes_sub, aes(x = Price))+
  geom_density(aes(color = City, fill = City), alpha = 0.3)+
  scale_x_continuous(limits = c(0, 3e6))

# Inside aes if referring to variable, outside aes if referring to constant

# alpha is transparency.. alpha 0 = transparent alpha 1 = totally opaque 
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and the point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price))+
  geom_point(aes(color = City, shape = Status))+
  geom_smooth(method = lm)
```

