---
title: "Lab 8"
author: "Anna Zauner"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(modelsummary)
library(broom)
```


```{r}
homes <- read_csv(here("data", "slo_homes.csv")) 
  
```

A little bit of cleaning:

Make a subset calles homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```


## Do a litle exploring of our data 

Summary statistics (home price, based on city and sale status)

Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status


```{r}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

## Actually I dont even wanna run this code: eval = FALSE

ggplot(data = homes_sub, aes(x = Price))+
  geom_density(aes(color = City, fill = City), alpha = 0.3)+
  scale_x_continuous(limits = c(0, 3e6))

# Inside aes if referring to variable, outside aes if referring to constant

# alpha is transparency.. alpha 0 = transparent alpha 1 = totally opaque 
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and the point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price))+
  geom_point(aes(color = City, shape = Status))+
  geom_smooth(method = lm)
```
## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitiative variables

homes_sub_1 <- homes %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_sub_1)

homes_cor

corrplot(homes_cor, method = 'ellipse')
```

## Refernces

- see by putting homes_lm1 into console 
- DOesnt make sense - additional bedrooms would decrease home price
                    - regular sale would be lower price than foreclosure
                    
- Should probably remove something... redundant 

```{r}
# How would I explore diagnostic plots?

plot(homes_lm1)
```

Try another model (homes_lm2) where we simplify this a but:
-City
-SqFt
-Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

# Or just call this in the console

homes_lm2

plot(homes_lm2)

# summary(homes_lm1) to look at R2 and p values 

# 0.84 R-squared means 84% of variance in price is explained by the predictor variables in this model (adjusted R squared for multiple linear agression to account for adding more variables)

# summmary(homes_lm2) look at outcomes

# Rsquared is 0.54 -- hmmm why is this lower than the first? we can compare looking with AIC (ideal model high fit and simple, worst model poor fit and complex)
```


Find the AIC value of each model

lower AIC means better balance between model fit and complexity 

Therefore, AIC lower is 1st. 

Concerns because 1st has bad variables, maybe there is an intermediate ?

```{r}
 AIC(homes_lm1)
AIC(homes_lm2)
```


```{r}
homes_lm3 <- lm(Price ~ City + Bedrooms + Status, data = homes_sub)

plot(homes_lm3)

summary(homes_lm3)

AIC(homes_lm3)
```
Use `modelsummary` to show model outputs side-by-side

If you use to return for multiple models, it wants a list

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model

Use `broom::augment()` 

```{r}
homes_predicted <- broom::augment(homes_lm1)
```


Use the `predict()` function to try out your model on new scenarios that you create. 

